Merging merges, more or less

### 2015-04-12 2015mergingmerges/section/05-Proofs.tex
proof attempts

@@

\begin{tabbing}
MM \= MM \= MM \= \kill
$\forall...$ \\
\>          \> $\EnvGrow{\Gamma}{p}{\Gamma'}$ \\
\> $\wedge$ \> $u~:_E~e~\in~\Gamma'$ \\
\> $\implies$\> $\bigcap\{e'~|~n~\Rightarrow~u~\in~m$ \\
\>           \>         \> $\wedge~\CheckOutTransUP{\Gamma'}{n}{u}{e'}$ \\
\>           \>         \> $\wedge~@exists path from p to u@\}$ \\
\> $\cap$ \> $\bigcap\{e' ~|~ u~:_E~e'~\in~\Gamma \} $ \\
\> $\cap$ \> $\bigcap\{e' ~|~ u~:_E~e'~\in~p \} $ \\
\> $=$       \> $e$
\end{tabbing}

We can proceed by induction over the closure.

(CloComputed):
regardless of whether $s~=~u$ or not, we simply use the induction hypothesis; since $a~=~b$, removing $s$ from $p$ does not change the result, as $s~:_E~a$ is left in $\Gamma$.

(CloRemoveOut):
again, we just use the induction hypothesis;
$s$ is removed from $\Gamma$ but the intersection of $\Gamma$'s $s$ and $p$'s $s$ is inserted into $p$.

(CloTransitions):
if $s~=~u$, the intersection is not affected as it is moved from $p$ to $\Gamma$.
If $u$ is one of the transitions from $s$, it is already in the first part of the intersection, so adding it to $p$ will not change the intersection.

(CloFinished):
here, $p$ is empty and there is no path from any elements of $p$ to $u$, so neither the first nor the last intersections have any effect, and the result is just $\Gamma$.

>>>>

We also define a predicate for checking whether there exists a path of transitions between two states of a machine.
\begin{tabbing}
MMMMMMM \= MM \= \kill
$@reachable@~m~u~v$ \\
\> $:=$
\> $u~=~v$ \\
\> $\wedge$ \> $\bigvee_{u'|u~\Rightarrow~u'}~@reachable@~m~u'~v$ \\
\end{tabbing}

@@

\begin{lemma}
Closure is intersection.

\begin{tabbing}
MM \= MM \= MM \= \kill
$\forall...$ \\
\>          \> $\EnvGrow{\Gamma}{p}{\Gamma'}$ \\
\> $\wedge$ \> $u~:_E~e~\in~\Gamma'$ \\
\> $\implies$\> $\bigcap\{e'~|~n~\Rightarrow~u~\in~m$ \\
\>           \>         \> $\wedge~\CheckOutTransUP{\Gamma'}{n}{u}{e'}$ \\
\>           \>         \> $\wedge~\bigvee_{v~\in~p}@reachable@~m~v~n\}$ \\
\> $\cap$ \> $\bigcap\{e' ~|~ u~:_E~e'~\in~\Gamma \} $ \\
\> $\cap$ \> $\bigcap\{e' ~|~ u~:_E~e'~\in~p \} $ \\
\> $=$       \> $e$
\end{tabbing}
\end{lemma}

\begin{proof}
By induction over the closure.

\begin{itemize}
\item \textbf{Case (CloComputed):}

regardless of whether $s~=~u$ or not, we simply use the induction hypothesis; since $a~=~b$, removing $s$ from $p$ does not change the result, as $s~:_E~a$ is left in $\Gamma$.

\item \textbf{Case (CloTransitions):}

if $s~=~u$, the intersection is not affected as it is moved from $p$ to $\Gamma$.
If $u$ is one of the transitions from $s$, it is already in the first part of the intersection, so adding it to $p$ will not change the intersection.

\item \textbf{Case (CloRemoveOut):}

again, we just use the induction hypothesis;
$s$ is removed from $\Gamma$ but the intersection of $\Gamma$'s $s$ and $p$'s $s$ is inserted into $p$.

\item \textbf{Case (CloFinished):}

here, $p$ is empty and there is no path from any elements of $p$ to $u$, so neither the first nor the last intersections have any effect, and the result is just $\Gamma$.
\end{itemize}

\end{proof}

Before we can prove that the result of merging satisfies invariants, we must show that the result of merging has an environment closure.
Computing the environment closure requires all transitions into a state to have the same event set, except for values of outputs.

\begin{lemma}
Likeness implies closure
\begin{tabbing}
MM \= MM \= MM \kill
 $~($
\> $\forall u ~|~ \bigcup_{q~\in~p~\cup~\Gamma}(@reachable@~m~q~u).$ \\
\> $\forall p_0 \in p~\cup~\Gamma.$ \\
\> $\forall p_1 \in p~\cup~\Gamma.$ \\
\> $\forall path_0 \in @path@~p_0~u.$ \\
\> $\forall path_1 \in @path@~p_1~u.$ \\
\> \> $path_0~:_E~\tau_0$ \\
\> $\wedge$ \> $path_1~:_E~\tau_1$ \\
\> $\implies$ \> $@like@~\tau_0~\tau_1)$ \\
$\implies$ \> $\exists \Gamma'.$ \> $\EnvGrow{\Gamma}{p}{\Gamma'}$ \\
\end{tabbing}
\end{lemma}

\begin{proof}
Induction over $\langle \card{@states@~m~\setminus~\Gamma},~\Sigma_{s~:_E~\tau~\in~\Gamma}\card{\tau},~\card{p} \rangle$, where $\langle \cdots \rangle$ is a lexicographic ordering.

\begin{description}
\item[Case $\langle 0,~0,~0 \rangle$]

$\card{p}~=~0 \implies p=\emptyset$

apply (CloFinished)

\item[Case $\langle g,~t,~y \rangle$]

destruct $p$
\begin{description}
\item[Case $\emptyset$]

apply (CloFinished)

\item[Case $s~:_E~\tau, p$]

destruct $s \in \Gamma$
\begin{description}
\item[Case false]

apply (CloTransitions).

apply i.h:

$\card{@states@~m~\setminus~(s~:_E~\tau, \Gamma)} < \card{@states@~m~\setminus~\Gamma}$

\item[Case $s~:_E~a~\in~\Gamma$]

destruct $a~=~\tau$
\begin{description}
\item[Case $a~=~\tau$]

apply (CloComputed):

$g$ same. $t$ same. $y$ decreases.

\item[Case $a~\not=~\tau$]

apply (CloUpdateTransitions).

$@like@~a~\tau$ from hypothesis.

$a~\not=~\tau~\implies~\card{a~\cap~\tau}~<~\card{a}$
\TODO{this is wrong}

$g$ same. $t$ decreases.
\end{description}
\end{description}
\end{description}
\end{description}

\end{proof}
